Weather Data MT

### 2024-06-13 qmd/projects/msu/wss/weatherdata.qmd
update

>>>>

```{r}
library(readxl)
lochy <-
read_excel("qmd/projects/msu/wss/weather/lochy_weather_scrape.xlsx")

line_table <-
lochy %>%
  dplyr::select(date, prcp) %>%
  mutate(month = month(date),
         day = day(date),
         year = as.factor(year(date))) %>%
  mutate(new_date = make_date(year = 0,
                              month = month,
                              day = day)) %>%
   mutate(category = case_when(new_date < "0000-07-15" ~ "pre",
                              new_date > "0000-09-15" ~ "post",
                              new_date >= "0000-07-15" & new_date <= "0000-09-15" ~ "mid")) %>%
  mutate(model_category = if_else(category == "mid", 
                                  "mid", "no"))

line_table_average <-
  line_table %>%
  group_by(month, day) %>%
  reframe(category, new_date,
          prcp = mean(prcp))

line_table %>%
  lm(prcp ~ model_category + year, data = .) %>%
  summary()

ggplot() +
  geom_line(aes(x = new_date, y = prcp),
            data = line_table_average %>%
              filter(category == "pre"),
            color = "black",
            linewidth = 0.25) +
  geom_line(aes(x = new_date, y = prcp),
            data = line_table_average %>%
              filter(category == "post"),
            color = "black",
            linewidth = 0.25) +
  geom_line(aes(x = new_date, y = prcp),
            data = line_table_average %>%
              filter(category == "mid"),
            color = "black") +
  geom_rect(aes(xmin = as.Date("0000-07-15", format = "%Y-%m-%d"),
                xmax = as.Date("0000-09-15", format = "%Y-%m-%d"),
                ymin = -0.01,
                ymax = 0.5),
            color = "Black",
            fill = "Blue",
            size = 0.3,
            alpha = 0.05,
            linetype = "solid") +
  labs(x = NULL,
       y = "Average Daily Precipitation (in)",
       color = NULL) +
  theme_bw()

  # geom_vline(xintercept = as.Date("0000-07-15", 
  #                                 format = "%Y-%m-%d"),
  #            linetype = "dashed",
  #            alpha = 0.5) +
  # geom_vline(xintercept = as.Date("0000-09-15", 
  #                                 format = "%Y-%m-%d"),
  #            linetype = "dashed",
  #            alpha = 0.5) +

bar_table <-
lochy %>%
  dplyr::select(date, prcp) %>%
  mutate(month = month(date),
         day = day(date),
         year = as.factor(year(date))) %>%
  mutate(new_date = make_date(year = 0,
                              month = month,
                              day = day)) %>%
  group_by(month) %>%
  mutate(prcp = mean(prcp, na.rm = TRUE))
```
